{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}

### 2016-09-30 sftrends_manu.Rnw
trends map added as figure

%knitr options
<<setup,include=F,cache=F>>=
library(knitr)
# set global chunk options
opts_chunk$set(fig.path = 'figs/', fig.align = 'center', fig.show = 'hold', message = F, echo = F, results = 'asis', dev = 'pdf', dev.args = list(family = 'serif'), fig.pos = '!ht', warning = F)
options(replace.assign = TRUE, width = 90, digits = 1)

@@

<<dinc10, fig.height = 8, fig.width = 7, out.width = '0.75\\textwidth', fig.cap = 'Time series of \\ac{din} and flow at station C10.  Subfigure (a) shows the observed \\ac{din} time series and subfigure (b) shows the annual (water year starting in October) predictions from \\ac{wrtds} at different conditional quantiles ($\\tau$ = 0.1, 0.5, 0.9).  The points in subfigure (b) are predictions of observed \\ac{din} and the lines are flow-normalized predictions.  Subfigure (c) shows the difference between the model predictions and flow-normalized predictions at the fiftieth conditional quantile.  Subfigure (d) shows the flow time series of the San Joaquin River with a locally-estimated (loess) smooth to emphasize the long-term trend.'>>=
# data
data(dinc10)

@@

# globals
ylab <- expression(paste('DIN (mg ', L^-1, ')'))
ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(),
    axis.line.y = element_line(), 
    axis.title.x = element_blank()
  )
col_vec <- RColorBrewer::brewer.pal(9, 'Set1')[c(3, 2, 1)]
col_lim <- c(0, 3.8)
xlims <- range(toplo$date)
txt <- data.frame(
  x = max(toplo$date), 
  y =  c(5, 2.4, 0.5, 7), 
  txt = c('(a)', '(b)', '(c)', '(d)')
)
size <- 7

# observed din
toplo1 <- select(toplo, date, res) %>% 
  na.omit()
p1 <- ggplot(toplo1, aes(x = date, y = exp(res))) + 
  geom_line() + 
  ptheme + 
  scale_y_continuous(ylab) +
  theme(
    axis.text.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, -24, 6), 'pt')
  ) +
  geom_text(data = txt[1, ], aes(x = x, y = y, label = txt), size = size) +
  scale_x_date(limits = xlims)

# din prdnrmplot
p2 <- prdnrmplot(toplo, logspace = F, col_vec = col_vec) + 
  ptheme + 
  scale_y_continuous(ylab) +
  theme(
    legend.position = 'top', 
    axis.text.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, -12, 6), 'pt')
  ) +
  geom_text(data = txt[2, ], aes(x = x, y = y, label = txt, colour = NULL), show.legend = F, size = size) +
  scale_x_date(limits = xlims)

# flo/observed diffs
toplo2 <- prdnrmplot(toplo, plot = F)
toplo2 <- left_join(toplo2$fits, toplo2$nrms, by = c('date', 'taus')) %>% 
  mutate(flodiff = fits_value - nrms_value) %>% 
  filter(taus == 0.5)
toplo3 <- toplo
toplo3$flo <- scales::rescale(toplo3$flo, to = attr(toplo, 'floobs_rng'))
ylab <- expression(paste('Pred - norm DIN (mg ', L^-1, ')'))
p3 <- ggplot(toplo2, aes(x = date, y = flodiff)) + 
  geom_bar(stat = 'identity') + 
  theme_minimal() +
  ptheme + 
  theme(
    axis.text.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, -12, 6), 'pt')
    ) + 
  scale_y_continuous(ylab) +
  scale_x_date(limits = xlims) +
  geom_text(data = txt[3, ], aes(x = x, y = y, label = txt), size = size)

@@

# globals
ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(),
    axis.line.y = element_line(), 
    axis.title.x = element_blank()
  )
col_lim <- c(0, 2.9)
txt <- data.frame(
  x = min(toplo$date), 
  y =  c(5, 2.4, 0.5, 6), 
  txt = c('a', 'b', 'c', 'd')
)
size <- 7

@@

ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(),
    axis.line.y = element_line(), 
    axis.title.x = element_blank()
  )
lncol <- RColorBrewer::brewer.pal(9, 'Set1')[2]

@@

# globals
ylab1 <- expression(paste(NO [2] ^ '-', ' / ', NO [3] ^ '2-', ' (mg ', L^-1, ')'))
ylab2 <- expression(paste(NH [4] ^ '+', ' (mg ', L^-1, ')'))
flolab <- expression(paste('ln-Flow (', m^3, ' ', s^-1, ')'))
ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(),
    axis.line.y = element_line()
  )
col_vec <- RColorBrewer::brewer.pal(9, 'Blues')[c(9, 8, 7)]
dynacol_vec <- RColorBrewer::brewer.pal(9, 'Spectral')
xlims <- range(nomod$date)

# observed time series
toplo1 <- select(nomod, date, res) %>% 
  na.omit()
toplo2 <- select(nhmod, date, res) %>% 
  na.omit()
p1 <- ggplot(toplo1, aes(x = date, y = exp(res))) + 
  geom_line() + 
  ptheme + 
  scale_y_continuous(ylab1) +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, -12, 6), 'pt')
  ) +
  # geom_text(data = txt[1, ], aes(x = x, y = y, label = txt), size = size) +
  scale_x_date(limits = xlims) 
p2 <- ggplot(toplo2, aes(x = date, y = exp(res))) + 
  geom_line() + 
  ptheme + 
  scale_y_continuous(ylab2) +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, -12, 6), 'pt')
  ) +
  # geom_text(data = txt[1, ], aes(x = x, y = y, label = txt), size = size) +
  scale_x_date(limits = xlims)

# prdnrmplots
p3 <- prdnrmplot(nomod, logspace = F, col_vec = col_vec, min_mo = 10) + 
  ptheme + 
  scale_y_continuous(ylab1) +
  theme(
    legend.position = 'top', 
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 6, 6), 'pt')
  ) +
  # geom_text(data = txt[2, ], aes(x = x, y = y, label = txt, colour = NULL), show.legend = F, size = size) +
  scale_x_date(limits = xlims) 
pleg1 <- g_legend(p3)
p3 <- p3 + theme(legend.position = 'none')
p4 <- prdnrmplot(nhmod, logspace = F, col_vec = col_vec, min_mo = 10) + 
  ptheme + 
  scale_y_continuous(ylab2) +
  theme(
    legend.position = 'none',
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 6, 6), 'pt')
  ) +
  # geom_text(data = txt[2, ], aes(x = x, y = y, label = txt, colour = NULL), show.legend = F, size = size) +
  scale_x_date(limits = xlims)

@@

grid.arrange(
  textGrob('(a) Observed, predicted, and flow-normalized trends'),
  arrangeGrob(pA, pB, ncol = 2), 
  pleg1,
  arrangeGrob(pC, pD, ncol = 2),
  textGrob('(b) Nutrient/flow relationships over time'),
  pleg2, 
  arrangeGrob(pE, pF, ncol = 2), 
  ncol = 1,
  heights = c(0.2, 0.8, 0.25, 1, 0.2, 0.25, 2)
  )
@

@@

##
# annual clam time series
p1 <- ggplot(clmdat, aes(x = yr, y = clams_smp, fill = species)) + 
  geom_bar(stat = 'identity') + 
  theme_minimal() + 
  theme(
    axis.line.y = element_line(), 
    axis.line.x = element_line(),
    # axis.title.x = element_blank(),
    legend.position = 'top', 
    legend.title = element_blank()
    ) + 
  scale_fill_brewer(
    palette = 'Set2',
    labels = parse(text = c('italic(Corbicula)', 'italic(Potamocorbula)'))
    ) + 
  scale_x_date('Year', limits = xlims) +
  scale_y_continuous('Clams per sample') +
  guides(fill = guide_legend(keywidth = 0.5, keyheight = 0.5)) +
  with(txt[1, ], annotate('text', x = xlims[1] + 365 * 2, y = y, label = txt, size = size))

@@

# scatter plot of concentration x biomass with model 
p2 <- ggplot(clmflo, aes(x = q, y = biomass)) + 
  geom_point(size = 3, alpha = 0.8, colour = 'darkgrey') + 
  geom_line(data = data.frame(x = xvals, y = yvals), aes(x, y, colour = 'black'), lwd = 1) +
  theme_minimal() + 
  theme(
    axis.line.y = element_line(), 
    axis.line.x = element_line(),
    legend.position = 'top', 
    legend.title = element_blank(), 
    legend.box = 'horizontal'
    ) +
  scale_colour_manual(label = 'log(1 + biomass) = 5.2 - 0.6log(1 + flow)', values = 'black') +
  scale_x_continuous(xlab) + 
  scale_y_continuous(ylab, limits = c(0,15)) +
  geom_text(data = txt[2, ], aes(x = x, y = y, label = txt, colour = NULL), show.legend = F, size = size)

@@

# scatter plot of concetration x biomass with model 
p3 <- ggplot(toplo, aes(x = biomass, y = bt_norm)) + 
  geom_point(size = 3, alpha = 0.8, colour = 'darkgrey') + 
  geom_line(data = data.frame(x = xvals, y = yvals), aes(x, y, colour = 'black'), lwd = 1) +
  theme_minimal() + 
  theme(
    axis.line.y = element_line(), 
    axis.line.x = element_line(),
    legend.position = 'top', 
    legend.title = element_blank(), 
    legend.box = 'horizontal'
    ) +
  scale_colour_manual(label = 'log(1 + chl) = 1.35 - 0.1log(1 + biomass)', values = 'black') +
  scale_x_continuous(xlab) + 
  scale_y_continuous(ylab, limits = c(0.8, 4)) +
  geom_text(data = txt[3, ], aes(x = x, y = y, label = txt, colour = NULL), show.legend = F, size = size)

@@

p4 <- dynaplot(chld7, mo = 6, col_vec = cols, floscl = F) +
  theme_minimal() +
  theme(
    axis.line.y = element_line(), 
    axis.line.x = element_line(),
    legend.position = 'top', 
    legend.title = element_blank(), 
    legend.box = 'horizontal',
    strip.background = element_blank(),
    strip.text.x = element_blank()
    ) + 
  scale_x_continuous('ln-Salinity (psu)') + 
  scale_y_continuous(ylab, limits = c(0.4, 3.3)) +
  guides(colour = guide_colourbar(barheight = 0.5, barwidth = 10)) + 
  annotate('text', x = txt[4, 'x'], y = txt[4, 'y'], label = txt[4, 'txt'], size = size)

@@

# generic theme for all plots
ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(),
    axis.line.y = element_line(), 
    axis.title.x = element_blank(), 
    axis.text.x = element_blank()
  )

>>>>

%knitr options
<<setup,include=F,cache=F>>=
library(knitr)
# set global chunk options
opts_chunk$set(fig.path = 'figs/', fig.align = 'center', fig.show = 'hold', message = F, echo = F, results = 'asis', dev = 'pdf', dev.args = list(family = 'serif'), fig.pos = '!ht', warning = F)
options(replace.assign = TRUE, width = 90)

@@

<<trends, fig.height = 6, fig.width = 7, out.width = '0.65\\textwidth', fig.cap = 'Percent changes in nitrogen analytes for (a) annual and (b) seasonal periods in the record.  Changes are based on the difference between the ending and starting estimates for the flow-normalized estimates within each period.  Points are colored for direction (red increasing, green decreasing) and sized for relative magnitude. Station names are shown in the top left panel.'>>=
trnd_map(molabs = NULL, sz_rng = c(2, 8), leg_lab = '(a) Annual % change')
trnd_map(yrlabs = NULL, sz_rng = c(2, 8), stat_labs = F, leg_lab = '(b) Seasonal % change')
@

<<dinc10, fig.height = 8, fig.width = 7, out.width = '0.75\\textwidth', fig.cap = 'Time series of \\ac{din} and flow at station C10.  Subfigure (a) shows the observed \\ac{din} time series and subfigure (b) shows the annual (water year starting in October) predictions from \\ac{wrtds} at different conditional quantiles ($\\tau$ = 0.1, 0.5, 0.9).  The points in subfigure (b) are predictions of observed \\ac{din} and the lines are flow-normalized predictions.  Subfigure (c) shows the difference between the model predictions and flow-normalized predictions at the fiftieth conditional quantile.  Subfigure (d) shows the flow time series of the San Joaquin River with a locally-estimated (loess) smooth to emphasize the long-term trend.'>>=

@@

# globals
ylab <- expression(paste('DIN (mg ', L^-1, ')'))
ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(),
    axis.line.y = element_line(), 
    axis.title.x = element_blank(),
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm") 
  )
col_vec <- RColorBrewer::brewer.pal(9, 'Set1')[c(3, 2, 1)]
col_lim <- c(0, 3.8)
xlims <- range(toplo$date)
txt <- data.frame(
  x = max(toplo$date), 
  y =  c(5, 2.4, 0.5, 7), 
  txt = c('(a)', '(b)', '(c)', '(d)')
)
size <- 7

# observed din
toplo1 <- select(toplo, date, res) %>% 
  na.omit()
p1 <- ggplot(toplo1, aes(x = date, y = exp(res))) + 
  geom_line() + 
  ptheme + 
  scale_y_continuous(ylab) +
  theme(
    axis.text.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 0, 6), 'pt')
  ) +
  geom_text(data = txt[1, ], aes(x = x, y = y, label = txt), size = size) +
  scale_x_date(limits = xlims)

# din prdnrmplot
p2 <- prdnrmplot(toplo, logspace = F, col_vec = col_vec) + 
  ptheme + 
  scale_y_continuous(ylab) +
  theme(
    legend.position = 'top', 
    axis.text.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 0, 6), 'pt')
  ) +
  geom_text(data = txt[2, ], aes(x = x, y = y, label = txt, colour = NULL), show.legend = F, size = size) +
  scale_x_date(limits = xlims)

# flo/observed diffs
toplo2 <- prdnrmplot(toplo, plot = F)
toplo2 <- left_join(toplo2$fits, toplo2$nrms, by = c('date', 'taus')) %>% 
  mutate(flodiff = fits_value - nrms_value) %>% 
  filter(taus == 0.5)
toplo3 <- toplo
toplo3$flo <- scales::rescale(toplo3$flo, to = attr(toplo, 'floobs_rng'))
ylab <- expression(paste('Pred - norm DIN (mg ', L^-1, ')'))
p3 <- ggplot(toplo2, aes(x = date, y = flodiff)) + 
  geom_bar(stat = 'identity') + 
  theme_minimal() +
  ptheme + 
  theme(
    axis.text.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 0, 6), 'pt')
    ) + 
  scale_y_continuous(ylab) +
  scale_x_date(limits = xlims) +
  geom_text(data = txt[3, ], aes(x = x, y = y, label = txt), size = size)

@@

# globals
ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm"),
    axis.title.x = element_blank()
  )
col_lim <- c(0, 2.9)
txt <- data.frame(
  x = min(toplo$date), 
  y =  c(5, 2.4, 0.5, 6), 
  txt = c('a', 'b', 'c', 'd')
)
size <- 7

@@

ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm"),
    axis.title.x = element_blank()
  )
lncol <- RColorBrewer::brewer.pal(9, 'Set1')[2]

@@

# globals
ylab1 <- expression(paste(NO [2] ^ '-', ' / ', NO [3] ^ '2-', ' (mg ', L^-1, ')'))
ylab2 <- expression(paste(NH [4] ^ '+', ' (mg ', L^-1, ')'))
flolab <- expression(paste('ln-Flow (', m^3, ' ', s^-1, ')'))
ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm")
  )
col_vec <- RColorBrewer::brewer.pal(9, 'Blues')[c(9, 8, 7)]
dynacol_vec <- RColorBrewer::brewer.pal(9, 'Spectral')
xlims <- range(nomod$date)

# observed time series
toplo1 <- select(nomod, date, res) %>% 
  na.omit()
toplo2 <- select(nhmod, date, res) %>% 
  na.omit()
p1 <- ggplot(toplo1, aes(x = date, y = exp(res))) + 
  geom_line() + 
  ptheme + 
  scale_y_continuous(ylab1) +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 0, 6), 'pt')
  ) +
  # geom_text(data = txt[1, ], aes(x = x, y = y, label = txt), size = size) +
  scale_x_date(limits = xlims) 
p2 <- ggplot(toplo2, aes(x = date, y = exp(res))) + 
  geom_line() + 
  ptheme + 
  scale_y_continuous(ylab2) +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 0, 6), 'pt')
  ) +
  # geom_text(data = txt[1, ], aes(x = x, y = y, label = txt), size = size) +
  scale_x_date(limits = xlims)

# prdnrmplots
p3 <- prdnrmplot(nomod, logspace = F, col_vec = col_vec, min_mo = 10) + 
  ptheme + 
  scale_y_continuous(ylab1) +
  theme(
    legend.position = 'top', 
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 0, 6), 'pt')
  ) +
  # geom_text(data = txt[2, ], aes(x = x, y = y, label = txt, colour = NULL), show.legend = F, size = size) +
  scale_x_date(limits = xlims) 
pleg1 <- g_legend(p3)
p3 <- p3 + theme(legend.position = 'none')
p4 <- prdnrmplot(nhmod, logspace = F, col_vec = col_vec, min_mo = 10) + 
  ptheme + 
  scale_y_continuous(ylab2) +
  theme(
    legend.position = 'none',
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 0, 6), 'pt')
  ) +
  # geom_text(data = txt[2, ], aes(x = x, y = y, label = txt, colour = NULL), show.legend = F, size = size) +
  scale_x_date(limits = xlims)

@@

grid.arrange(
  textGrob('(a) Observed, predicted, and flow-normalized trends'),
  arrangeGrob(pA, pB, ncol = 2), 
  pleg1,
  arrangeGrob(pC, pD, ncol = 2),
  textGrob('(b) Nutrient/flow relationships over time'),
  pleg2, 
  arrangeGrob(pE, pF, ncol = 2), 
  ncol = 1,
  heights = c(0.2, 0.8, 0.25, 0.9, 0.2, 0.25, 2)
  )
@

@@

##
# annual clam time series
p1 <- ggplot(clmdat, aes(x = yr, y = clams_smp, fill = species)) + 
  geom_bar(stat = 'identity') + 
  theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm"), 
    # axis.title.x = element_blank(),
    legend.position = 'top', 
    legend.title = element_blank()
    ) + 
  scale_fill_brewer(
    palette = 'Set2',
    labels = parse(text = c('italic(Corbicula)', 'italic(Potamocorbula)'))
    ) + 
  scale_x_date('Year', limits = xlims) +
  scale_y_continuous('Clams per sample') +
  guides(fill = guide_legend(keywidth = 0.5, keyheight = 0.5)) +
  with(txt[1, ], annotate('text', x = xlims[1] + 365 * 2, y = y, label = txt, size = size))

@@

# scatter plot of concentration x biomass with model 
p2 <- ggplot(clmflo, aes(x = q, y = biomass)) + 
  geom_point(size = 3, alpha = 0.8, colour = 'darkgrey') + 
  geom_line(data = data.frame(x = xvals, y = yvals), aes(x, y, colour = 'black'), lwd = 1) +
  theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm"), 
    legend.position = 'top', 
    legend.title = element_blank(), 
    legend.box = 'horizontal'
    ) +
  scale_colour_manual(label = 'log(1 + biomass) = 5.2 - 0.6log(1 + flow)', values = 'black') +
  scale_x_continuous(xlab) + 
  scale_y_continuous(ylab, limits = c(0,15)) +
  geom_text(data = txt[2, ], aes(x = x, y = y, label = txt, colour = NULL), show.legend = F, size = size)

@@

# scatter plot of concetration x biomass with model 
p3 <- ggplot(toplo, aes(x = biomass, y = bt_norm)) + 
  geom_point(size = 3, alpha = 0.8, colour = 'darkgrey') + 
  geom_line(data = data.frame(x = xvals, y = yvals), aes(x, y, colour = 'black'), lwd = 1) +
  theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm"),
    legend.position = 'top', 
    legend.title = element_blank(), 
    legend.box = 'horizontal'
    ) +
  scale_colour_manual(label = 'log(1 + chl) = 1.35 - 0.1log(1 + biomass)', values = 'black') +
  scale_x_continuous(xlab) + 
  scale_y_continuous(ylab, limits = c(0.8, 4)) +
  geom_text(data = txt[3, ], aes(x = x, y = y, label = txt, colour = NULL), show.legend = F, size = size)

@@

p4 <- dynaplot(chld7, mo = 6, col_vec = cols, floscl = F) +
  theme_minimal() +
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm"),
    legend.position = 'top', 
    legend.title = element_blank(), 
    legend.box = 'horizontal',
    strip.background = element_blank(),
    strip.text.x = element_blank()
    ) + 
  scale_x_continuous('ln-Salinity (psu)') + 
  scale_y_continuous(ylab, limits = c(0.4, 3.3)) +
  guides(colour = guide_colourbar(barheight = 0.5, barwidth = 10)) + 
  annotate('text', x = txt[4, 'x'], y = txt[4, 'y'], label = txt[4, 'txt'], size = size)

@@

# generic theme for all plots
ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm"),  
    axis.title.x = element_blank(), 
    axis.text.x = element_blank()
  )

### 2016-09-30 sftrends_manu.tex
trends map added as figure

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, David Senn$^2$, Phil Bresnahan$^2$, Emily Novick$^2$, James D. Hagy III$^1$,}}
  \\{\bf {\normalsize Thomas Jabusch$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:hagy.jim@epa.gov}{hagy.jim@epa.gov}}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Avenue, Richmond, CA 94804}}
	\\{\textit {\normalsize Phone: 510-746-7334, Fax: 510-746-7300}}
	\\{\textit {\normalsize Emails: \href{mailto:davids@sfei.org}{davids@sfei.org}, \href{mailto:philb@sfei.org}{philb@sfei.org}, \href{mailto:emilyn@sfei.org}{emilyn@sfei.org}, \href{mailto:thomasj@sfei.org}{thomasj@sfei.org}}}
  \vspace{1in} 
  \\ Version Date:   Tue Jul 19 17:50:17 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

>>>>

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, David Senn$^2$, Phil Bresnahan$^2$, Emily Novick$^2$, James D. Hagy III$^1$,}}
  \\{\bf {\normalsize Thomas Jabusch$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:hagy.jim@epa.gov}{hagy.jim@epa.gov}}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Avenue, Richmond, CA 94804}}
	\\{\textit {\normalsize Phone: 510-746-7334, Fax: 510-746-7300}}
	\\{\textit {\normalsize Emails: \href{mailto:davids@sfei.org}{davids@sfei.org}, \href{mailto:philb@sfei.org}{philb@sfei.org}, \href{mailto:emilyn@sfei.org}{emilyn@sfei.org}, \href{mailto:thomasj@sfei.org}{thomasj@sfei.org}}}
  \vspace{1in} 
  \\ Version Date:   Wed Jul 20 11:11:39 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

{\centering \includegraphics[width=0.65\textwidth]{figs/trends-1} 
\includegraphics[width=0.65\textwidth]{figs/trends-2}

\caption[Percent changes in nitrogen analytes for (a) annual and (b) seasonal periods in the record]{Percent changes in nitrogen analytes for (a) annual and (b) seasonal periods in the record.  Changes are based on the difference between the ending and starting estimates for the flow-normalized estimates within each period.  Points are colored for direction (red increasing, green decreasing) and sized for relative magnitude. Station names are shown in the top left panel.}\label{fig:trends}
\end{figure}
